A boundary-integral framework to simulate \\ viscous erosion of a porous medium

### 2018-04-16 docs/methods/erosion_methods.tex
NM
moved bibliography to .tex file

\paragraph{Related Work}
In a closely related study, Mitchell \& Spagnolie used a traction integral equation formulation to simulate the viscous erosion of a single body in three dimensions~\cite{mit-spa2016}. The flexibility of this formulation enabled simulations of a {\em mobile} body eroding in an {\em aribtrary} background flow (e.g.~uniform flow, shear flow, etc.).  An advantage of the traction formulation is that it directly provides the shear stress needed to evolve surfaces.  In the present work, we aim to simulate the erosion of a porous medium and, further, choose to fix the bodies to their initial locations. Thus, rather than a {\em single, mobile} body as considered in~\cite{mit-spa2016}, we aim to simulate the erosion of {\em many, immobile} bodies. Although the traction formulation has several attractive features, we instead employ a standard double-layer formulation since it allows us to easily calculate bulk quantities (e.g.~vorticity, pressure, and velocity) that will assist our understanding of the erosion process.

For the porous network simulations considered here, it is essential to resolve nonlocal effects between the different bodies.  BIEs naturally resolve these interactions, and they have been used extensively to simulate viscous fluids in complex geometries, including porous media flow~\cite{dea-qua-bir-jua2018, bar-mar-vee-zha2018}.  Common challenges of a BIE formulation include developing efficient preconditioners for the discretized system and numerical difficulties associated with nearly touching bodies. In this work, we consider geometries requiring $\mathcal{O}(100)$ GMRES iterations, so preconditioners are currently unnecessary. In future work, we will address mobile bodies for which near contacts may necessitate preconditoners~\cite{qua-bir2015a, qua-cou-dar2018, cou-pou-dar2017}. Similarly, near-singular schemes will not be necessary due to the fact that the spacing between receding bodies of fixed position always grows in time. Again, the future consideration of mobile bodies may necessitate near-singular schemes~\cite{qua-bir2014a, klo-bar-gre-one2013, bar-wu-vee2015, hel-oja2008a, bea-lai2001}.

@@

To numerically compute the completed double-layer potential~\eqref{eqn:completed_BIE}, we discretize each of the $M$ bodies with  $N_\iin$ points, and the outer boundary with $N_\out$ points.  Then, $N = MN_\iin + N_\out$ is the total number of discretization points of $\bd\Omega$.  The double-layer potential in~\eqref{eqn:DLP} is discretized with the trapezoid rule as
\begin{align}
  \DD[\eeta](\xx_i) = \sum_{j=1}^{N} K(\xx_i,\xx_j) \eeta(\xx_j) 
      \Delta s_{j}\, , \quad i=1,\ldots,N \, ,
  \label{eqn:trapDLP}
\end{align}
where $\Delta s_j$ is the arclength term of $\bd\Omega$ at
$\xx_j$, and
\begin{align}
  K(\xx,\yy) = \frac{1}{\pi} \frac{\rr \cdot \nn}{\rho^2} 
      \frac{\rr \otimes \rr}{\rho^2} \, ,
\end{align}
where $\rr = \xx - \yy$ and $\rho = \|\rr\|$, is the kernel of the double-layer potential.  The diagonal term of~\eqref{eqn:trapDLP} is replaced with the limiting value of the double-layer potential
\begin{align}
  D(\xx,\xx) = -\frac{\kappa(\xx)}{2\pi}(\ss(\xx) \otimes \ss(\xx)) \, ,
\end{align}
where $\kappa(\xx)$ is the curvature and $\ss(\xx)$ is the unit tangent vector at $\xx \in \bd\Omega$.  The equations for the Stokeslets~\eqref{eqn:stokeslet} and the rotlets~\eqref{eqn:rotlet} are also discretized with the trapezoid rule.  Applying this discretization strategy to~\eqref{eqn:completed_BIE}, the dense linear system to be solved is
\begin{subequations}
  \label{eqn:completed_BIE_discretized}
  \begin{align}
  \label{eqn:discretized_DLP}
    \ff(\xx_i) &= -\frac{1}{2}\ssigma(\xx_i) + \sum_{j=1}^{N} 
      K(\xx_i,\xx_j) \eeta(\xx_j) \Delta s_{j} + 
      \sum_{\ell=1}^M S[\llambda_\ell,\cc_\ell](\xx_i) +
      \sum_{\ell=1}^M R[\xi_\ell,\cc_\ell](\xx_i) \\
    \llambda_\ell &= \sum_{\xx_j \in \gamma_\ell} \eeta(\xx_j) 
      \Delta s_j \, , \\ 
    \xi_\ell &= \sum_{\xx_j \in \gamma_\ell}
      {(\xx_j - \cc_\ell)}^\perp \cdot \eeta(\xx_j) \Delta s_j \, ,
  \end{align}
\end{subequations}
for $i=1,\ldots,N$, $\ell=1,\ldots,M$.  When $\xx_i \in \Gamma$, the term 
\begin{align}
  \sum_{\xx_j \in \Gamma} (\nn(\xx_i) \otimes
      \nn(\xx_j))\eeta(\xx_j) \, ,
\end{align}
is added to~\eqref{eqn:discretized_DLP}.  Since we discetize integrands that are smooth and periodic, the trapezoid rule employed above achieves spectral accuracy~\cite{tre-wei2014}.

@@

To validate the multibody simulations with this new fixed-pressure-drop condition, we report a convergence test in Table~\ref{convtab2}. In this test, we simulate the erosion of 20 bodies to a stopping time of $t_s = 4 \times 10^{-3}$. This stopping time is 24\% of the time required for {\em all} bodies to vanish, and, in fact, a few of the bodies will have already vanished by $t_s$. To assess error, we measure the aggregate $L^2$-difference in the shape of {\em all} of the bodies, comparing simulations of successive temporal resolution. Note that this metric is sensitive to numerical errors in any of the simulated bodies. The table confirms that our method retains second-order accuracy in time, thus validating our rescaling procedure and confirming that multibody interactions are handled correctly by the Stokes solver. The last column of the table shows the computational time of each simulation, demonstrating a linear increase with temporal resolution. Naturally, these 20-body simulations require significantly more CPU time than do the single-body simulations.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{\bf Acknowledgments} We would like to thank Manas Rachh for supplying the FMM for the Stokes double-layer potential. 
%We would like to thank Saverio Spagnolie, William Mitchell, Daniel Rothman, Michael Shelley, ....

\bibliographystyle{plainnat} 
\bibliography{refs}
\biboptions{sort&compress}
\end{document}

>>>>

\paragraph{Related Work}
In a closely related study, Mitchell \& Spagnolie used a traction integral equation formulation to simulate the viscous erosion of a single body in three dimensions~\cite{mit-spa2016}. The flexibility of this formulation enabled simulations of a {\em mobile} body eroding in an {\em arbitrary} background flow (e.g.~uniform flow, shear flow, etc.).  An advantage of the traction formulation is that it directly provides the shear stress needed to evolve surfaces.  In the present work, we aim to simulate the erosion of a porous medium and, further, choose to fix the bodies to their initial locations. Thus, rather than a {\em single, mobile} body as considered in~\cite{mit-spa2016}, we aim to simulate the erosion of {\em many, immobile} bodies. Although the traction formulation has several attractive features, we instead employ a standard double-layer formulation since it allows us to easily calculate bulk quantities (e.g.~vorticity, pressure, and velocity) that will assist our understanding of the erosion process.

For the porous network simulations considered here, it is essential to
resolve nonlocal effects between the different bodies.  BIEs naturally
resolve these interactions, and they have been used extensively to
simulate viscous fluids in complex geometries, including porous media
flow~\cite{dea-qua-bir-jua2018, bar-mar-vee-zha2018}.  Common challenges
of a BIE formulation include developing efficient preconditioners for
the discretized system and numerical difficulties associated with nearly
touching bodies. In this work, we consider geometries requiring
$\mathcal{O}(100)$ GMRES iterations, so preconditioners are currently
unnecessary. In future work, we will address mobile bodies for which
near contacts may necessitate preconditioners~\cite{qua-bir2015a, qua-cou-dar2018, cou-pou-dar2017}. Similarly, near-singular schemes will not be necessary due to the fact that the spacing between receding bodies of fixed position always grows in time. Again, the future consideration of mobile bodies may necessitate near-singular schemes~\cite{qua-bir2014a, klo-bar-gre-one2013, bar-wu-vee2015, hel-oja2008a, bea-lai2001}.

@@

To numerically compute the completed double-layer potential~\eqref{eqn:completed_BIE}, we discretize each of the $M$ bodies with  $N_\iin$ points, and the outer boundary with $N_\out$ points.  Then, $N = MN_\iin + N_\out$ is the total number of discretization points of $\bd\Omega$.  The double-layer potential in~\eqref{eqn:DLP} is discretized with the trapezoid rule as
\begin{align}
  \DD[\eeta](\xx_i) = \sum_{j=1}^{N} K(\xx_i,\xx_j) \eeta(\xx_j) 
      \Delta s_{j}\, , \quad i=1,\ldots,N \, ,
  \label{eqn:trapDLP}
\end{align}
where $\Delta s_j$ is the arclength term of $\bd\Omega$ at
$\xx_j$, and
\begin{align}
  K(\xx,\yy) = \frac{1}{\pi} \frac{\rr \cdot \nn}{\rho^2} 
      \frac{\rr \otimes \rr}{\rho^2} \, ,
\end{align}
where $\rr = \xx - \yy$ and $\rho = \|\rr\|$, is the kernel of the double-layer potential.  The diagonal term of~\eqref{eqn:trapDLP} is replaced with the limiting value of the double-layer potential
\begin{align}
  D(\xx,\xx) = -\frac{\kappa(\xx)}{2\pi}(\ss(\xx) \otimes \ss(\xx)) \, ,
\end{align}
where $\kappa(\xx)$ is the curvature and $\ss(\xx)$ is the unit tangent vector at $\xx \in \bd\Omega$.  The equations for the Stokeslets~\eqref{eqn:stokeslet} and the rotlets~\eqref{eqn:rotlet} are also discretized with the trapezoid rule.  Applying this discretization strategy to~\eqref{eqn:completed_BIE}, the dense linear system to be solved is
\begin{subequations}
  \label{eqn:completed_BIE_discretized}
  \begin{align}
  \label{eqn:discretized_DLP}
    \ff(\xx_i) &= -\frac{1}{2}\ssigma(\xx_i) + \sum_{j=1}^{N} 
      K(\xx_i,\xx_j) \eeta(\xx_j) \Delta s_{j} + 
      \sum_{\ell=1}^M S[\llambda_\ell,\cc_\ell](\xx_i) +
      \sum_{\ell=1}^M R[\xi_\ell,\cc_\ell](\xx_i) \\
    \llambda_\ell &= \sum_{\xx_j \in \gamma_\ell} \eeta(\xx_j) 
      \Delta s_j \, , \\ 
    \xi_\ell &= \sum_{\xx_j \in \gamma_\ell}
      {(\xx_j - \cc_\ell)}^\perp \cdot \eeta(\xx_j) \Delta s_j \, ,
  \end{align}
\end{subequations}
for $i=1,\ldots,N$, $\ell=1,\ldots,M$.  When $\xx_i \in \Gamma$, the term 
\begin{align}
  \sum_{\xx_j \in \Gamma} (\nn(\xx_i) \otimes
      \nn(\xx_j))\eeta(\xx_j) \, ,
\end{align}
is added to~\eqref{eqn:discretized_DLP}.  Since we discretize integrands that are smooth and periodic, the trapezoid rule employed above achieves spectral accuracy~\cite{tre-wei2014}.

@@

To validate the multibody simulations with this new fixed-pressure-drop condition, we report a convergence test in Table~\ref{convtab2}. In this test, we simulate the erosion of 20 bodies to a stopping time of $t_s = 4 \times 10^{-3}$. This stopping time is 24\% of the time required for {\em all} bodies to vanish, and, in fact, a few of the bodies will have already vanished by $t_s$. To assess error, we measure the aggregate $L^2$-difference in the shape of {\em all} of the bodies, comparing simulations of successive temporal resolution. Note that this metric is sensitive to numerical errors in any of the simulated bodies. The table confirms that our method retains second-order accuracy in time, thus validating our rescaling procedure and confirming that multibody interactions are handled correctly by the Stokes solver. The last column of the table shows the computational time of each simulation, demonstrating a linear increase with refinement of the time step. Naturally, these 20-body simulations require significantly more CPU time than do the single-body simulations.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{\bf Acknowledgments} We would like to thank Manas Rachh for supplying the FMM for the Stokes double-layer potential.

\bibliographystyle{plainnat} 
\biboptions{sort&compress}

\begin{thebibliography}{72}
\providecommand{\natexlab}[1]{#1}
\providecommand{\url}[1]{\texttt{#1}}
\expandafter\ifx\csname urlstyle\endcsname\relax
  \providecommand{\doi}[1]{doi: #1}\else
  \providecommand{\doi}{doi: \begingroup \urlstyle{rm}\Url}\fi

\bibitem[Abrams et~al.(2009)Abrams, Lobkovsky, Petroff, Straub, McElroy,
  Mohrig, Kudrolli, and Rothman]{abrams2009growth}
Daniel~M Abrams, Alexander~E Lobkovsky, Alexander~P Petroff, Kyle~M Straub,
  Brandon McElroy, David~C Mohrig, Arshad Kudrolli, and Daniel~H Rothman.
\newblock Growth laws for channel networks incised by groundwater flow.
\newblock \emph{Nature Geoscience}, 2\penalty0 (3):\penalty0 193, 2009.

\bibitem[af~Klinteberg and Tornberg(2016)]{kli-tor2016b}
Ludvig af~Klinteberg and Anna-Karin Tornberg.
\newblock A fast integral equation method for solid particles in viscous flow
  using quadrature by expansion.
\newblock \emph{Journal of Computational Physics}, 326:\penalty0 420--445,
  2016.

\bibitem[Barnett et~al.(2015)Barnett, Wu, and Veerapaneni]{bar-wu-vee2015}
Alex Barnett, Bowei Wu, and Shravan Veerapaneni.
\newblock {Spectrally-Accurate Quadratures for Evaluation of Layer Potentials
  Close to the Boundary for the 2D Stokes and Laplace Equations}.
\newblock \emph{SIAM Journal on Scientific Computing}, 37\penalty0
  (4):\penalty0 B519--B542, 2015.

\bibitem[Barnett et~al.(2018)Barnett, Marple, Veerapaneni, and
  Zhao]{bar-mar-vee-zha2018}
Alex Barnett, Gary Marple, Shravan Veerapaneni, and Lin Zhao.
\newblock {A unified integral equation scheme for doubly-periodic Laplace and
  Stokes boundary value problems in two dimensions}.
\newblock \emph{Communications on Pure and Applied Mathematic}, 2018.
\newblock In press.

\bibitem[Barnett(2014)]{bar2014}
Alex~H. Barnett.
\newblock {Evaluation of layer potentials close to the boundary for Laplace and
  Helmholtz problems on analytic planar domains}.
\newblock \emph{SIAM Journal on Scientific Computing}, 36\penalty0
  (2):\penalty0 A427--A451, 2014.

\bibitem[Batchelor(1970)]{batchelor1970slender}
GK~Batchelor.
\newblock {Slender-body theory for particles of arbitrary cross-section in
  Stokes flow}.
\newblock \emph{Journal of Fluid Mechanics}, 44\penalty0 (3):\penalty0
  419--440, 1970.

\bibitem[Beale and Lai(2001)]{bea-lai2001}
J.T. Beale and M.-C. Lai.
\newblock {A Method for Computing Nearly Singular Integrals}.
\newblock \emph{SIAM Journal on Numerical Analysis}, 38\penalty0 (6):\penalty0
  1902--1925, 2001.

\bibitem[Bear(2013)]{bear2013dynamics}
Jacob Bear.
\newblock \emph{Dynamics of fluids in porous media}.
\newblock Courier Corporation, 2013.

\bibitem[Berhanu et~al.(2012)Berhanu, Petroff, Devauchelle, Kudrolli, and
  Rothman]{berhanu2012shape}
Michael Berhanu, Alexander Petroff, Olivier Devauchelle, Arshad Kudrolli, and
  Daniel~H Rothman.
\newblock Shape and dynamics of seepage erosion in a horizontal granular bed.
\newblock \emph{Physical Review E}, 86\penalty0 (4):\penalty0 041304, 2012.

\bibitem[Bremer(2012)]{bre2012}
James Bremer.
\newblock {On the Nystr\"om discretization of integral equations on planar
  curves with corners}.
\newblock \emph{Applied and Computational Harmonic Analysis}, 32:\penalty0
  45--64, 2012.

\bibitem[Camassa et~al.(2012)Camassa, McLaughlin, Moore, and Yu]{MooreJFM2012}
R.~Camassa, R.M. McLaughlin, M.N.J. Moore, and K.~Yu.
\newblock Stratified flows with vertical layering of density: experimental and
  theoretical study of flow configurations and their stability.
\newblock \emph{Journal of Fluid Mechanics}, 690:\penalty0 571--606, 2012.

\bibitem[Campbell et~al.(1996)Campbell, Ipsen, Kelley, Meyer, and
  Xue]{cam-ips-kel-mey-xue1996}
S.~L. Campbell, I.~C.~F. Ipsen, C.~T. Kelley, C.~D. Meyer, and Z.~Q. Xue.
\newblock {Convergence estimates for solution of integral equations with
  GMRES}.
\newblock \emph{Journal of Integral Equations and Applications}, 8\penalty0
  (1):\penalty0 19--34, 1996.

\bibitem[Cao et~al.(2010)Cao, Gunzburger, Hua, Wang, et~al.]{cao2010coupled}
Yanzhao Cao, Max Gunzburger, Fei Hua, Xiaoming Wang, et~al.
\newblock Coupled stokes-darcy model with beavers-joseph interface boundary
  condition.
\newblock \emph{Communications in Mathematical Sciences}, 8\penalty0
  (1):\penalty0 1--25, 2010.

\bibitem[Claudin et~al.(2017)Claudin, Dur{\'a}n, and
  Andreotti]{claudin2017dissolution}
Philippe Claudin, Orencio Dur{\'a}n, and Bruno Andreotti.
\newblock Dissolution instability and roughening transition.
\newblock \emph{Journal of Fluid Mechanics}, 832, 2017.

\bibitem[Cohen et~al.(2016)Cohen, Berhanu, Derr, and du~Pont]{cohen2016erosion}
Caroline Cohen, Michael Berhanu, Julien Derr, and Sylvain~Courrech du~Pont.
\newblock Erosion patterns on dissolving and melting bodies.
\newblock \emph{Physical Review Fluids}, 1\penalty0 (5):\penalty0 050508, 2016.

\bibitem[Cohen et~al.(2015)Cohen, Devauchelle, Seybold, Yi, Szymczak, and
  Rothman]{coh-dev-sey-yi-szy-rot2015}
Yossi Cohen, Olivier Devauchelle, Hansj{\"o}rg~F. Seybold, Robert~S. Yi, Piotr
  Szymczak, and Daniel~H. Rothman.
\newblock Path selection in the growth of rivers.
\newblock \emph{Proceedings of the National Academy of Sciences}, 112\penalty0
  (46):\penalty0 14132--14137, 2015.

\bibitem[Corona and Veerapaneni(2017)]{cor-vee2017}
Eduardo Corona and Shravan Veerapaneni.
\newblock {Boundary integral equation analysis for suspension of spheres in
  Stokes flow}.
\newblock \emph{arxiv}, 1707.06551, 2017.

\bibitem[Corona et~al.(2017)Corona, Greengard, Rachh, and
  Veerapaneni]{cor-gre-rac-vee2017}
Eduardo Corona, Leslie Greengard, Manas Rachh, and Shravan Veerapaneni.
\newblock {An integral equation formulation for rigid bodies in Stokes flow in
  three dimensions}.
\newblock \emph{Journal of Computational Physics}, 332:\penalty0 504--519,
  2017.

\bibitem[Coulier et~al.(2017)Coulier, Pouransari, and Darve]{cou-pou-dar2017}
Pieter Coulier, Hadi Pouransari, and Eric Darve.
\newblock {The Inverse Fast Multipole Method: Using a Fast Approximate Diret
  Solver as a Preconditioner for Dense Linear Systems}.
\newblock \emph{SIAM Journal on Scientific Computing}, 39\penalty0
  (3):\penalty0 A761--A796, 2017.

\bibitem[Daerr et~al.(2003)Daerr, Lee, Lanuza, and
  Cl{\'e}ment]{daerr2003erosion}
Adrian Daerr, Peter Lee, Jos{\'e} Lanuza, and {\'E}ric Cl{\'e}ment.
\newblock Erosion patterns in a sediment layer.
\newblock \emph{Physical Review E}, 67\penalty0 (6):\penalty0 065201, 2003.

\bibitem[Dallaston et~al.(2015)Dallaston, Hewitt, and
  Wells]{dallaston2015channelization}
MC~Dallaston, IJ~Hewitt, and AJ~Wells.
\newblock Channelization of plumes beneath ice shelves.
\newblock \emph{Journal of Fluid Mechanics}, 785:\penalty0 109--134, 2015.

\bibitem[de~Anna et~al.(2018)de~Anna, Quaife, Biros, and
  Juanes]{dea-qua-bir-jua2018}
Pietro de~Anna, Bryan Quaife, George Biros, and Ruben Juanes.
\newblock {Prediction of velocity distribution from pore structure in simple
  porous media}.
\newblock \emph{Physical Review Fluids}, 2\penalty0 (12):\penalty0 124103,
  2018.

\bibitem[Devauchelle et~al.(2012)Devauchelle, Petroff, Seybold, and
  Rothman]{Rothman2012}
O.~Devauchelle, A.P. Petroff, H.F. Seybold, and D.H. Rothman.
\newblock Ramification of stream networks.
\newblock \emph{Proceedings of the National Academy of Sciences}, 109\penalty0
  (51):\penalty0 20832--20836, 2012.

\bibitem[Domokos et~al.(2014)Domokos, Jerolmack, Sipos, and
  T{\"o}r{\"o}k]{domokos2014river}
Gabor Domokos, Douglas~J Jerolmack, Andras~{\'A} Sipos, and {\'A}kos
  T{\"o}r{\"o}k.
\newblock How river rocks round: resolving the shape-size paradox.
\newblock \emph{PloS One}, 9\penalty0 (2):\penalty0 e88657, 2014.

\bibitem[Gillman et~al.(2014)Gillman, Hao, and Martinsson]{gil-hao-mar2014}
A.~Gillman, S.~Hao, and P.G. Martinsson.
\newblock {A simplified technique for the efficient and highly accurate
  discretization of boundary integral equations in 2D on domains with corners}.
\newblock \emph{Journal of Computational Physics}, 256:\penalty0 214--219,
  2014.

\bibitem[Greenbaum et~al.(1992)Greenbaum, Greengard, and Mayo]{gre-gre-may1992}
Anne Greenbaum, Leslie Greengard, and Anita Mayo.
\newblock On the numerical solution of the biharmonic equation in the plane.
\newblock \emph{Physica D: Nonlinear Phenomena}, 60:\penalty0 216--225, 1992.

\bibitem[Greengard and Rokhlin(1987)]{gre-rok1987}
L.~Greengard and V.~Rokhlin.
\newblock {A Fast Algorithm for Particle Simulations}.
\newblock \emph{Journal of Computational Physics}, 73:\penalty0 325--348, 1987.

\bibitem[Greengard et~al.(1996)Greengard, Kropinski, and Mayo]{gre-kro-may1996}
L.~Greengard, M.C. Kropinski, and A.~Mayo.
\newblock {Integral Equation Methods for Stokes Flow and Isotropic Elasticity
  in the Plane}.
\newblock \emph{Journal of Computational Physics}, 125\penalty0 (2):\penalty0
  403--414, 1996.

\bibitem[Groen et~al.(2007)Groen, Gijsen, van~der Lugt, Ferguson, Hatsukami,
  van~der Steen, Yuan, and Wentzel]{gro-gij-van-fer-hat-van-yua-wen2007}
Harald~C. Groen, Frank~J.H. Gijsen, Aad van~der Lugt, Marina~S. Ferguson,
  Thomas~S. Hatsukami, Anton~F.W. van~der Steen, Chun Yuan, and Jolanda~J.
  Wentzel.
\newblock {Plaque Rupture in the Carotid Artery Is Localized at the High Shear
  Stress Region: A Case Report}.
\newblock \emph{Stroke}, 38:\penalty0 2379--2381, 2007.

\bibitem[Hanna(1969)]{han1969}
Steven~R. Hanna.
\newblock {The Formation of Longitudinal Sand Dunes by Large Helical Eddies in
  the Atmosphere}.
\newblock \emph{Journal of Applied Meteorology}, 8\penalty0 (6):\penalty0
  874--883, 1969.

\bibitem[Helsing(2011)]{hel2011}
J.~Helsing.
\newblock {A Fast and Stable Solver for Singular Integral Equations and
  Piecewise Smooth Curves}.
\newblock \emph{SIAM Journal on Scientific Comuting}, 33:\penalty0 153--174,
  2011.

\bibitem[Helsing and Ojala(2008)]{hel-oja2008a}
Johan Helsing and Rikard Ojala.
\newblock On the evaluation of layer potentials close to their sources.
\newblock \emph{Journal of Computational Physics}, 227:\penalty0 2899--2921,
  2008.

\bibitem[Hewett and Sellier(2017{\natexlab{a}})]{hewett2017evolution}
James~N Hewett and Mathieu Sellier.
\newblock Evolution of an eroding cylinder in single and lattice arrangements.
\newblock \emph{Journal of Fluids and Structures}, 70:\penalty0 295--313,
  2017{\natexlab{a}}.

\bibitem[Hewett and Sellier(2017{\natexlab{b}})]{hewett2017pear}
James~N Hewett and Mathieu Sellier.
\newblock The pear-shaped fate of an ice melting front.
\newblock \emph{arXiv preprint arXiv:1705.02536}, 2017{\natexlab{b}}.

\bibitem[Hou et~al.(1994)Hou, Lowengrub, and Shelley]{hou-low-she1994}
Thomas~Y. Hou, John~S. Lowengrub, and Michael~J. Shelley.
\newblock {Removing the Stiffness for Interfacial Flows with Surface Tension}.
\newblock \emph{Journal of Computational Physics}, 114:\penalty0 312--338,
  1994.

\bibitem[Huang et~al.(2015)Huang, Moore, and Ristroph]{Huang2015}
J.~M. Huang, M.N.J. Moore, and L.~Ristroph.
\newblock Shape dynamics and scaling laws for a body dissolving in fluid flow.
\newblock \emph{Journal of Fluid Mechanics}, 765, 2 2015.
\newblock ISSN 1469-7645.

\bibitem[Jerolmack et~al.(2012)Jerolmack, Ewing, Falcini, Martin, Masteller,
  Phillips, Reitz, and Buynevich]{jerolmack2012internal}
Douglas~J Jerolmack, Ryan~C Ewing, Federico Falcini, Raleigh~L Martin, Claire
  Masteller, Colin Phillips, Meredith~D Reitz, and Ilya Buynevich.
\newblock Internal boundary layer model for the evolution of desert dune
  fields.
\newblock \emph{Nature Geoscience}, 5\penalty0 (3):\penalty0 206, 2012.

\bibitem[Kabacao\u{g}lu et~al.(2018)Kabacao\u{g}lu, Quaife, and
  Biros]{kab-qua-bir2018}
Gokberk Kabacao\u{g}lu, Bryan Quaife, and George Biros.
\newblock {Low-resolution simulations of vesicle suspensions in 2D}.
\newblock \emph{Journal of Computational Physics}, 357:\penalty0 43--77, 2018.

\bibitem[Kl\"{o}ckner et~al.(2013)Kl\"{o}ckner, Barnett, Greengard, and
  O'Neil]{klo-bar-gre-one2013}
Andreas Kl\"{o}ckner, Alexander Barnett, Leslie Greengard, and Michael O'Neil.
\newblock {Quadrature by expansion: A new method for the evaluation of layer
  potentials}.
\newblock \emph{Journal of Computational Physics}, 252:\penalty0 332--349,
  2013.

\bibitem[Kondratiuk and Szymczak(2015)]{kondratiuk2015steadily}
Pawe{\l} Kondratiuk and Piotr Szymczak.
\newblock {Steadily Translating Parabolic Dissolution Fingers}.
\newblock \emph{SIAM Journal on Applied Mathematics}, 75\penalty0 (5):\penalty0
  2193--2213, 2015.

\bibitem[Ladyzhenskaya(1963)]{lad1963}
O.~A. Ladyzhenskaya.
\newblock \emph{{The Mathematical Theory of Viscous Incompressible Flow}}.
\newblock Gordon and Breach Science, 1963.

\bibitem[L{\'o}pez et~al.(2018)L{\'o}pez, Stickland, and
  Dempster]{lopez2018cfd}
Alejandro L{\'o}pez, Matthew~T Stickland, and William~M Dempster.
\newblock Cfd study of fluid flow changes with erosion.
\newblock \emph{Computer Physics Communications}, 2018.

\bibitem[Lu et~al.(2017)Lu, Rahimian, and Zorin]{lu-rah-zor2017}
Libin Lu, Abtin Rahimian, and Denis Zorin.
\newblock {Contact-aware simulations of particulate Stokesian suspensions}.
\newblock \emph{Journal of Computational Physics}, 347:\penalty0 160--182,
  2017.

\bibitem[Mitchell and Spagnolie(2016)]{mit-spa2016}
W.H. Mitchell and S.E. Spagnolie.
\newblock A generalized traction integral equation for {S}tokes flow, with
  applications to near-wall particle mobility and viscous erosion.
\newblock \emph{Journal of Computational Physics}, 2016.

\bibitem[Moore(2017)]{moore2017riemann}
M~Nicholas~J Moore.
\newblock {Riemann-Hilbert Problems for the Shapes Formed by Bodies Dissolving,
  Melting, and Eroding in Fluid Flows}.
\newblock \emph{Communications on Pure and Applied Mathematics}, 70\penalty0
  (9):\penalty0 1810--1831, 2017.

\bibitem[Moore et~al.(2013)Moore, Ristroph, Childress, Zhang, and
  Shelley]{moo-ris-chi-zha-she2013}
Matthew N.~J. Moore, Leif Ristroph, Stephen Childress, Jun Zhang, and
  Michael~J. Shelley.
\newblock Self-similar evolution of a body eroding in a fluid flow.
\newblock \emph{Physics of Fluids}, 25:\penalty0 116602, 2013.

\bibitem[Nienhuis et~al.(2014)Nienhuis, Perron, Kao, and
  Myrow]{nienhuis2014wavelength}
Jaap~H Nienhuis, J~Taylor Perron, Justin~CT Kao, and Paul~M Myrow.
\newblock Wavelength selection and symmetry breaking in orbital wave ripples.
\newblock \emph{Journal of Geophysical Research: Earth Surface}, 119\penalty0
  (10):\penalty0 2239--2257, 2014.

\bibitem[O.Pironneau(1973)]{pir1973}
O.Pironneau.
\newblock {On optimum profiles in Stokes flow}.
\newblock \emph{Journal of Fluid Mehanics}, 59\penalty0 (1):\penalty0 117--128,
  1973.

\bibitem[Perkins et~al.(2015)Perkins, Finnegan, and
  De~Silva]{perkins2015amplification}
Jonathan~P Perkins, Noah~J Finnegan, and Shanaka~L De~Silva.
\newblock Amplification of bedrock canyon incision by wind.
\newblock \emph{Nature Geoscience}, 8\penalty0 (4):\penalty0 305, 2015.

\bibitem[Perron et~al.(2009)Perron, Kirchner, and
  Dietrich]{perron2009formation}
J~Taylor Perron, James~W Kirchner, and William~E Dietrich.
\newblock Formation of evenly spaced ridges and valleys.
\newblock \emph{Nature}, 460\penalty0 (7254):\penalty0 502, 2009.

\bibitem[Petroff et~al.(2011)Petroff, Devauchelle, Abrams, Lobkovsky, Kudrolli,
  and Rothman]{petroff2011geometry}
Alexander~P Petroff, Olivier Devauchelle, Daniel~M Abrams, Alexander~E
  Lobkovsky, Arshad Kudrolli, and Daniel~H Rothman.
\newblock Geometry of valley growth.
\newblock \emph{Journal of Fluid Mechanics}, 673:\penalty0 245--254, 2011.

\bibitem[Picioreanu et~al.(2001)Picioreanu, van Loosdrecht, and
  Heijnen]{pic-van-hei2000}
Cristian Picioreanu, Mark C.~M. van Loosdrecht, and Joseph~J. Heijnen.
\newblock {Two-Dimensional Model of Biofilm Detachment Caused by Internal
  Stress from Liquid Flow}.
\newblock \emph{Biotechnology and Bioengineering}, 72\penalty0 (2):\penalty0
  205--218, 2001.

\bibitem[Power(1993)]{pow1993}
H.~Power.
\newblock {The completed double layer boundary integral equation method for
  two-dimensional Stokes flow}.
\newblock \emph{IMA Journal of Applied Mathematics}, 51\penalty0 (2):\penalty0
  123--145, 1993.

\bibitem[Power and Miranda(1987)]{pow-mir1987}
H.~Power and G.~Miranda.
\newblock Second kind integral equation formulation of stokes' flows past a
  particle of arbitrary shape.
\newblock \emph{SIAM Journal on Applied Mathematics}, 47\penalty0 (4):\penalty0
  689--698, 1987.

\bibitem[Pozrikidis(1992)]{poz1992}
C.~Pozrikidis.
\newblock \emph{{Boundary Integral and Singularity Methods for Linearized
  Viscous Flow}}.
\newblock Cambridge University Press, New York, NY, USA, 1992.

\bibitem[Pozrikidis(1997)]{poz1997}
C.~Pozrikidis.
\newblock \emph{Introduction to Theoretical and Computational Fluid Dynamics}.
\newblock Oxford University Press, New York, 1997.

\bibitem[Quaife and Biros(2014)]{qua-bir2014a}
Bryan Quaife and George Biros.
\newblock High-volume fraction simulations of two-dimensional vesicle
  suspensions.
\newblock \emph{Journal of Computational Physics}, 274:\penalty0 245--267,
  2014.

\bibitem[Quaife and Biros(2015)]{qua-bir2015a}
Bryan Quaife and George Biros.
\newblock {On preconditioners for the Laplace double-layer potential in 2D}.
\newblock \emph{Numerical Linear Algebra with Applications}, 22:\penalty0
  101--122, 2015.

\bibitem[Quaife and Biros(2016)]{qua-bir2016}
Bryan Quaife and George Biros.
\newblock {Adaptive time stepping for vesicle simulations}.
\newblock \emph{Journal of Computational Physics}, 306:\penalty0 478--499,
  2016.

\bibitem[Quaife et~al.(2018)Quaife, Coulier, and Darve]{qua-cou-dar2018}
Bryan Quaife, Pieter Coulier, and Eric Darve.
\newblock {An efficient preconditioner for the fast simulation of a 2D Stokes
  flow in porous media}.
\newblock \emph{International Journal for Numerical Methods in Engineering},
  113:\penalty0 561--580, 2018.

\bibitem[Rachh and Serkh(2017)]{rac-ser2017}
M.~Rachh and K.~Serkh.
\newblock {On the solution of Stokes equation on regions with corners}.
\newblock \emph{arxiv}, 1711.04072, 2017.

\bibitem[Rachh and Greengard(2016)]{rac-gre2016}
Manas Rachh and L.~Greengard.
\newblock Integral equation methods for elastance and mobility problems in two
  dimensions.
\newblock \emph{SIAM Journal on Numerical Analysis}, 54\penalty0 (5):\penalty0
  2889--2909, 2016.

\bibitem[Ristroph(2018)]{ristroph2018sculpting}
Leif Ristroph.
\newblock Sculpting with flow.
\newblock \emph{Journal of Fluid Mechanics}, 838:\penalty0 1--4, 2018.
